---
title: "01_exclusion"
output: html_document
date: '2022-04-01'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library
```{r Library}
library(formr)
library(dplyr)
library(tidyr)
```

## Load data
```{r Load data}
data_wrangled = read.csv(file = "data/data_wrangled.csv")[,-1]
```

## Exclusion criteria
### For main analyses
Following the order the criteria were listed in the preregistration
1. Excluding participants not identifying as women
```{r Exlcusion criterion 1}
data_wrangled_main = data_wrangled %>%
  filter(sex == "Woman")

nrow(data_wrangled_main) # 64879 women 
```

2. Excluding participants not identifying as asexual or heterosexual
```{r Excluison criterion 2}
data_wrangled_main = data_wrangled_main %>% 
  filter(sexual_orientation == "Straight/Heterosexual" | sexual_orientation == "Asexual")

nrow(data_wrangled_main) # 53390 women 
table(data_wrangled_main$sexual_orientation) # 457 asexuals and 52933 heterosexuals
```

3. Excluding participants choosing not to answer the honesty question or indicating not having filled out the survey truthfully
```{r Exclusion criterion 3}
data_wrangled_main = data_wrangled_main %>% 
 mutate(answer_accuracy = replace_na(answer_accuracy, "No value"))
data_wrangled_main = data_wrangled_main %>%
  filter(answer_accuracy == "I took the survey seriously; please use my information in the study." | answer_accuracy == "No value")

nrow(data_wrangled_main) # 51775 women 
table(data_wrangled_main$sexual_orientation) # 447 asexuals and 51328 heterosexuals

table(is.na(data_wrangled_main$answer_accuracy))
table(data_wrangled_main$answer_accuracy)
```

### For robustness check
1. Excluding participants not identifying as women, man or genderqueer/nonbinary
```{r Criterion 1 robustness}
data_wrangled_robustness = data_wrangled %>%
  filter(sex == "Woman" | sex == "Man" | sex == "Genderqueer/Nonbinary")

nrow(data_wrangled_robustness) # 67774 participants 
```

2. Excluding participants not identifying as asexual or heterosexual
```{r Criterion 2 robustness}
data_wrangled_robustness = data_wrangled_robustness %>% 
  filter(sexual_orientation == "Straight/Heterosexual" | sexual_orientation == "Asexual")

nrow(data_wrangled_robustness) # 55076 participants
table(data_wrangled_robustness$sexual_orientation) # 539 asexuals and 54537 heterosexuals
```

3. Excluding participants choosing not to answer the honesty question or indicating not having filled out the survey truthfully
```{r Criterion 3 robustness}
data_wrangled_robustness = data_wrangled_robustness %>% 
 mutate(answer_accuracy = replace_na(answer_accuracy, "No value"))
data_wrangled_robustness = data_wrangled_robustness %>%
  filter(answer_accuracy == "I took the survey seriously; please use my information in the study." | answer_accuracy == "No value")

nrow(data_wrangled_robustness) # 53412 women 
table(data_wrangled_robustness$sexual_orientation) # 527 asexuals and 46913 heterosexuals

```

## Total number of excluded participants
```{r}
# for main analyses
nrow(data_wrangled) - nrow(data_wrangled_main)

# for robustness check
nrow(data_wrangled) - nrow(data_wrangled_robustness)
```

## Save data
### For main analyses
```{r Save data main analyses}
# write.csv(data_wrangled_main,
#          file = "data_main.csv")
```

### For robustness check
```{r Save data robustness check}
# write.csv(data_wrangled_robustness,
#          file = "data_robustness.csv")
```
  
