---
title: "05_comparison_all_groups"
output: html_document
date: '2022-05-16'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Comparison of Asexuals, matched heterosexuals, and unmatched heterosexuals in all covariates and outcomes

## Library
```{r}
library(dplyr)
library(formr)
library(ggplot2)
library(psych)
```

## Load data
```{r}
# matched samples
data_rel = read.csv(file = "data/data_rel.csv")[,-1]
data_prefs = read.csv(file = "data/data_prefs.csv")[,-1]
data_self = read.csv(file = "data/data_self.csv")[,-1]

# unmatched heterosexual sample (includes only heterosexuals because during psm no asexual was discarded)
data_rel_unmatched = read.csv(file = "data/data_rel_unmatched.csv")[,-1]
data_prefs_unmatched = read.csv(file = "data/data_prefs_unmatched.csv")[,-1]
data_self_unmatched = read.csv(file = "data/data_self_unmatched.csv")[,-1]

nrow(data_rel_unmatched)
describe.by(asex_v_umhetero_rel, asex_v_umhetero_rel$sexual_orientation)
nrow(data_prefs_unmatched)
describe.by(asex_v_umhetero_prefs, asex_v_umhetero_prefs$sexual_orientation)

# asexual sample 
asexuals_rel = data_rel %>% filter(sexual_orientation == "Asexual")
asexuals_prefs = data_prefs %>% filter(sexual_orientation == "Asexual")
asexuals_self = data_self %>% filter(sexual_orientation == "Asexual")

# matched heterosexual sample (also from partner preference psm sample)
heterosexuals_rel = data_rel %>%  filter(sexual_orientation == "Straight/Heterosexual")
heterosexuals_prefs = data_prefs %>%  filter(sexual_orientation == "Straight/Heterosexual")
heterosexuals_self = data_self %>%  filter(sexual_orientation == "Straight/Heterosexual")
```


## Create samples for each comparison:
```{r  }
# Asexuals v. matched heterosexuals: 
asex_v_hetero_rel = data_rel
asex_v_hetero_prefs = data_prefs
asex_v_hetero_self = data_self

# Asexuals v. unmatched heterosexuals:
asex_v_umhetero_rel = full_join(asexuals_rel, data_rel_unmatched)
asex_v_umhetero_prefs = full_join(asexuals_prefs, data_prefs_unmatched)
asex_v_umhetero_self = full_join(asexuals_self, data_self_unmatched)

# Matched heterosexuals v. unmatched heterosexuals:
# add variable matched (matched or unmatched) as grouping variable to data sets
data_rel_unmatched$matched = "unmatched"
heterosexuals_rel$matched = "matched"

data_prefs_unmatched$matched = "unmatched"
heterosexuals_prefs$matched = "matched"

data_self_unmatched$matched = "unmatched"
heterosexuals_self$matched = "matched"

# merge data sets
hetero_v_umhetero_rel = full_join(heterosexuals_rel, data_rel_unmatched)
hetero_v_umhetero_prefs = full_join(heterosexuals_prefs, data_prefs_unmatched)
hetero_v_umhetero_self = full_join(heterosexuals_self, data_self_unmatched)
```


## 0. Descriptives for unmatched Heterosexuals (for asexuals and matched heterosexuals descriptives have been computed before - see 05_descriptives_psm.Rmd)
### 0.1 Covariates (based on partner preference sample)
```{r}
# quick overview 
describe.by(data_prefs_unmatched)
```

#### Country
```{r}
sort(table(data_prefs_unmatched$country), decreasing = T) # absolute numbers
sort(round(table(data_prefs_unmatched$country)/sum(table(data_prefs_unmatched$country)),4)*100, decreasing = T) # in percent
```

#### Language
```{r}
sort(table(data_prefs_unmatched$language), decreasing = T) # absolute numbers
sort(round(table(data_prefs_unmatched$language)/sum(table(data_prefs_unmatched$language)),4)*100, decreasing = T) # in percent
```

#### Age
```{r}
# mean, sd, min, max
data_prefs_unmatched %>%
  summarise(mean(age, na.rm = T), 
            min(age, na.rm = T), 
            max(age, na.rm = T),
            sd(age, na.rm = T))


# Histogram 
ggplot(data_prefs_unmatched, aes(x = age, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")
```

#### Relationship status
```{r}
sort(table(data_prefs_unmatched$relationship_status), decreasing = T) # absolute numbers
sort(round(table(data_prefs_unmatched$relationship_status)/sum(table(data_prefs_unmatched$relationship_status)),4)*100, decreasing = T) # in percent
```

#### Relationship length 
```{r}
# mean, sd, min, max
data_prefs_unmatched %>%
  summarise(mean(relationship_length, na.rm = T), 
            min(relationship_length, na.rm = T), 
            max(relationship_length, na.rm = T),
            sd(relationship_length, na.rm = T))


# Histogram by group 
ggplot(data_prefs, aes(x = relationship_length, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")
```




## 1. Asexuals v. matched heterosexuals
## Sort matched data by subclass number within sexual_orientation (for dependent t-test order of observation matters)
```{r}
data_rel = data_rel %>% 
        group_by(sexual_orientation) %>%
        arrange(subclass, .by_group = TRUE)

data_prefs = data_prefs %>% 
        group_by(sexual_orientation) %>%
        arrange(subclass, .by_group = TRUE)

data_self = data_self %>% 
        group_by(sexual_orientation) %>%
        arrange(subclass, .by_group = TRUE)
```

### Covariates
#### Country
```{r}
chisq_country = chisq.test(data_prefs$sexual_orientation, data_prefs$country) 
chisq_country
chisq_country$observed
round(chisq_country$expected,2)


library(rcompanion)
# calculate Cramer's V
asexual = data_prefs %>%  filter(sexual_orientation == "Asexual") %>% 
  select(country)
heterosexual = data_prefs %>% filter(sexual_orientation == "Straight/Heterosexual") %>% 
  select(country)
cramerV(asexual$country, heterosexual$country)
```

#### language
```{r}
chisq_language = chisq.test(data_prefs$sexual_orientation, data_prefs$language) 
chisq_language
chisq_language$observed
round(chisq_language$expected,2)
```

#### Age
```{r}
t.test(age ~ sexual_orientation, data = data_prefs,
       alternative = "two.sided",
       paired = TRUE)

# effect size
effsize::cohen.d(age ~ sexual_orientation, data = data_prefs, paired = TRUE)
```

#### Relationship status
```{r}
chisq_relstat = chisq.test(data_prefs$sexual_orientation, data_prefs$relationship_status) 
chisq_relstat
chisq_relstat$observed
round(chisq_relstat$expected,2)
```

#### Relationship length
```{r}
t.test(relationship_length ~ sexual_orientation, data = data_prefs,
       alternative = "two.sided",
       paired = TRUE)

# effect size
effsize::cohen.d(relationship_length ~ sexual_orientation, data = data_prefs, paired = TRUE)
```

### Outcomes == Analysen
```{r}

```


## 2. Asexuals vs. unmatched heterosexuals
### Covariates
#### Country
```{r}
country_asex_v_umhetero = chisq.test(asex_v_umhetero$sexual_orientation, asex_v_umhetero$country)
country_asex_v_umhetero
country_asex_v_umhetero$observed
round(country_asex_v_umhetero$expected,2)
```

#### language
```{r}
language_asex_v_umhetero = chisq.test(asex_v_umhetero$sexual_orientation, asex_v_umhetero$language)
language_asex_v_umhetero
language_asex_v_umhetero$observed
round(language_asex_v_umhetero$expected,2)
```

#### Age
```{r}
t.test(age ~ sexual_orientation, data = asex_v_umhetero,
       alternative = "two.sided",
       paired = FALSE)

# effect size
effsize::cohen.d(age ~ sexual_orientation, data = asex_v_umhetero, paired = FALSE)
```

#### Relationship status
```{r}
relstat_asex_v_umhetero = chisq.test(asex_v_umhetero$sexual_orientation, asex_v_umhetero$relationship_status)
relstat_asex_v_umhetero
relstat_asex_v_umhetero$observed
round(relstat_asex_v_umhetero$expected,2)
```

#### Relationship length
```{r}
t.test(relationship_length ~ sexual_orientation, data = asex_v_umhetero,
       alternative = "two.sided",
       paired = FALSE)

# effect size
effsize::cohen.d(relationship_length ~ sexual_orientation, data = asex_v_umhetero, paired = FALSE)
```

### Outcomes
#### Ideal partner preferences
```{r}
# quick overview
describe.by(asex_v_umhetero_prefs, asex_v_umhetero_prefs$sexual_orientation)
```

##### confident-assertive
```{r}
t.test(pref_imp_ca ~ sexual_orientation, 
       data = asex_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_ca ~ sexual_orientation, data = asex_v_umhetero_prefs, paired = FALSE)
```

##### attractive
```{r}
t.test(pref_imp_att ~ sexual_orientation, 
       data = asex_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_att ~ sexual_orientation, data = asex_v_umhetero_prefs, paired = FALSE)
```

##### sexually experienced
```{r}
t.test(pref_imp_sexually_experienced ~ sexual_orientation, 
       data = asex_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_sexually_experienced ~ sexual_orientation, data = asex_v_umhetero_prefs, paired = FALSE)
```

##### kind-supportive
```{r}
t.test(pref_imp_ks ~ sexual_orientation, 
       data = asex_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_ks ~ sexual_orientation, data = asex_v_umhetero_prefs, paired = FALSE)
```


##### financially-secure/successfull
```{r}
t.test(pref_imp_fs ~ sexual_orientation, 
       data = asex_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_fs ~ sexual_orientation, data = asex_v_umhetero_prefs, paired = FALSE)
```


##### educated-intelligent
```{r}
t.test(pref_imp_ei ~ sexual_orientation, 
       data = asex_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_ei ~ sexual_orientation, data = asex_v_umhetero_prefs, paired = FALSE)
```

#### Self-ratings
```{r}
# quick overview
describe.by(asex_v_umhetero_self, asex_v_umhetero_self$sexual_orientation)
```

##### confident-assertive
```{r}
t.test(self_ca ~ sexual_orientation, 
       data = asex_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_ca ~ sexual_orientation, data = asex_v_umhetero_self, paired = FALSE)
```

##### attractive
```{r}
t.test(self_att ~ sexual_orientation, 
       data = asex_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_att ~ sexual_orientation, data = asex_v_umhetero_self, paired = FALSE)
```

##### sexually experienced
```{r}
t.test(self_sexually_experienced ~ sexual_orientation, 
       data = asex_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_sexually_experienced ~ sexual_orientation, data = asex_v_umhetero_self, paired = FALSE)
```

##### kind-supportive
```{r}
t.test(self_ks ~ sexual_orientation, 
       data = asex_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_ks ~ sexual_orientation, data = asex_v_umhetero_self, paired = FALSE)
```


##### financially-secure/successfull
```{r}
t.test(self_fs ~ sexual_orientation, 
       data = asex_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_fs ~ sexual_orientation, data = asex_v_umhetero_self, paired = FALSE)
```


##### educated-intelligent
```{r}
t.test(self_ei ~ sexual_orientation, 
       data = asex_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_ei ~ sexual_orientation, data = asex_v_umhetero_self, paired = FALSE)
```


#### Preferred relationship options
```{r}
# quick overview
describe.by(asex_v_umhetero_rel, asex_v_umhetero_rel$sexual_orientation)
```

##### interest non-sexual relationships
```{r}
t.test(interest_nonsexrel ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)

# effect size
effsize::cohen.d(interest_nonsexrel ~ sexual_orientation, data = asex_v_umhetero_rel , paired = F)
```

##### interest sexual relationships
```{r}
t.test(interest_hookups ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_hookups ~ sexual_orientation, data = data_rel, paired = F)
```

##### interest non-monogamous relationships
```{r}
t.test(interest_nonmonrel ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_nonmonrel ~ sexual_orientation, data = asex_v_umhetero_rel, paired = F)
```

##### interest alternativ committed relationships
```{r}
t.test(interest_altrel ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_altrel ~ sexual_orientation, data = asex_v_umhetero_rel, paired = F)
```

##### interest single
```{r}
t.test(interest_single ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_single ~ sexual_orientation, data = asex_v_umhetero_rel, paired = F)
```

##### interest monogamous relationships
```{r}
t.test(interest_monrel ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_monrel ~ sexual_orientation, data = asex_v_umhetero_rel, paired = F)
```

##### interest parent 
```{r}
t.test(interest_parent ~ sexual_orientation, 
       data = asex_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_parent ~ sexual_orientation, data = asex_v_umhetero_rel, paired = F)
```




## 3. Matched heterosexuals v. unmatched heterosexuals
### Covariates
#### Country
```{r}
country_hetero_v_umhetero = chisq.test(hetero_v_umhetero_prefs$country)
country_hetero_v_umhetero
country_hetero_v_umhetero$observed
round(country_hetero_v_umhetero$expected,2)
```

#### language
```{r}
language_hetero_v_umhetero = chisq.test(hetero_v_umhetero_prefs$matched, hetero_v_umhetero_prefs$language)
language_hetero_v_umhetero
language_hetero_v_umhetero$observed
round(language_hetero_v_umhetero$expected,2)
```

#### Age
```{r}
t.test(age ~ matched, data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)

# effect size
effsize::cohen.d(age ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```

#### Relationship status
```{r}
relstat_hetero_v_umhetero = chisq.test(hetero_v_umhetero_prefs$matched, hetero_v_umhetero_prefs$relationship_status)
relstat_hetero_v_umhetero
relstat_hetero_v_umhetero$observed
round(relstat_hetero_v_umhetero$expected,2)
```

#### Relationship length
```{r}
t.test(relationship_length ~ matched, data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)

# effect size
effsize::cohen.d(relationship_length ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```

### Outcomes
#### Ideal partner preferences
```{r}
# quick overview
describe.by(hetero_v_umhetero_prefs, hetero_v_umhetero_prefs$matched) 
```

##### confident-assertive
```{r}
t.test(pref_imp_ca ~ matched, 
       data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_ca ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```

##### attractive
```{r}
t.test(pref_imp_att ~ matched, 
       data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_att ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```

##### sexually experienced
```{r}
t.test(pref_imp_sexually_experienced ~ matched, 
       data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_sexually_experienced ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```

##### kind-supportive
```{r}
t.test(pref_imp_ks ~ matched, 
       data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_ks ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```


##### financially-secure/successfull
```{r}
t.test(pref_imp_fs ~ matched, 
       data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_fs ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```


##### educated-intelligent
```{r}
t.test(pref_imp_ei ~ matched, 
       data = hetero_v_umhetero_prefs,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(pref_imp_ei ~ matched, data = hetero_v_umhetero_prefs, paired = FALSE)
```

#### Self-ratings
```{r}
# quick overview
describe.by(hetero_v_umhetero_self, hetero_v_umhetero_self$matched) 
```

##### confident-assertive
```{r}
t.test(self_ca ~ matched, 
       data = hetero_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_ca ~ matched, data = hetero_v_umhetero_self, paired = FALSE)
```

##### attractive
```{r}
t.test(self_att ~ matched, 
       data = hetero_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_att ~ matched, data = hetero_v_umhetero_self, paired = FALSE)
```

##### sexually experienced
```{r}
t.test(self_sexually_experienced ~ matched, 
       data = hetero_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_sexually_experienced ~ matched, data = hetero_v_umhetero_self, paired = FALSE)
```

##### kind-supportive
```{r}
t.test(self_ks ~ matched, 
       data = hetero_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_ks ~ matched, data = hetero_v_umhetero_self, paired = FALSE)
```


##### financially-secure/successfull
```{r}
t.test(self_fs ~ matched, 
       data = hetero_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_fs ~ matched, data = hetero_v_umhetero_self, paired = FALSE)
```


##### educated-intelligent
```{r}
t.test(self_ei ~ matched, 
       data = hetero_v_umhetero_self,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(self_ei ~ matched, data = hetero_v_umhetero_self, paired = FALSE)
```

#### Preferred relationship options
```{r}
# quick overview
describe(hetero_v_umhetero_rel)
```

##### interest non-sexual relationships
```{r}
t.test(interest_nonsexrel ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)

# effect size
effsize::cohen.d(interest_nonsexrel ~ matched, data = hetero_v_umhetero_rel , paired = F)
```

##### interest sexual relationships
```{r}
t.test(interest_hookups ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_hookups ~ sexual_orientation, data = data_rel, paired = F)
```

##### interest non-monogamous relationships
```{r}
t.test(interest_nonmonrel ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_nonmonrel ~ matched, data = hetero_v_umhetero_rel, paired = F)
```

##### interest alternativ committed relationships
```{r}
t.test(interest_altrel ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_altrel ~ matched, data = hetero_v_umhetero_rel, paired = F)
```

##### interest single
```{r}
t.test(interest_single ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_single ~ matched, data = hetero_v_umhetero_rel, paired = F)
```

##### interest monogamous relationships
```{r}
t.test(interest_monrel ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_monrel ~ matched, data = hetero_v_umhetero_rel, paired = F)
```

##### interest parent 
```{r}
t.test(interest_parent ~ matched, 
       data = hetero_v_umhetero_rel,
       alternative = "two.sided",
       paired = FALSE)


# effect size
effsize::cohen.d(interest_parent ~ matched, data = hetero_v_umhetero_rel, paired = F)
```

