---
title: "05_descriptives_psm"
output: html_document
date: '2022-04-19'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Descriptives for propensity-score-matched samples

## Library
```{r}
library(dplyr)
library(formr)
library(ggplot2)
library(psych)
library(apaTables)
```

## Load data
```{r}
data_rel = read.csv(file = "data/data_rel.csv")[,-1]
data_prefs = read.csv(file = "data/data_prefs.csv")[,-1]
data_self = read.csv(file = "data/data_self.csv")[,-1]
```

## 1. Relationship options
### Descriptives for whole sample
#### Demographic data
##### Sexual orientation
```{r}
table(data_rel$sexual_orientation) # sexual orientation in absolute numbers
round(table(data_rel$sexual_orientation)/sum(table(data_rel$sexual_orientation)),4)*100 # sexual orientation in percent
table(is.na(data_rel$sexual_orientation)) # no NAs 
```

##### Country
```{r}
table(data_rel$country) # country in absolute numbers
round(table(data_rel$country)/sum(table(data_rel$country)),4)*100 # country in percent
table(is.na(data_rel$country)) # no NAs 
```

##### Language
Chinese, Danish, English, French, German, Japanese, Portuguese, Russian, Spanish, Italian
```{r Language}
table(data_rel$language) # language in absolute numbers
round(table(data_rel$language)/sum(table(data_rel$language)),4)*100 # country in percent
table(is.na(data_rel$language)) #no NAs
```

##### Age
```{r}
table(data_rel$age)
range(data_rel$age, na.rm = T) # range
table(is.na(data_rel$age)) # NAs

# histogram 
hist(data_rel$age)

# mean, sd
round(mean(data_rel$age, na.rm = T),2)
round(sd(data_rel$age, na.rm = T),2)

# median
median(data_rel$age)
```

##### Sex 
```{r Sex}
table(data_rel$sex) # in absolute numbers
round(table(data_rel$sex)/sum(table(data_rel$sex)),4)*100 # in percent
table(is.na(data_rel$sex))
```

##### Relationship status
```{r}
table(data_rel$relationship_status) # in absolute numbers
round(table(data_rel$relationship_status)/sum(table(data_rel$relationship_status)),4)*100 # in percent
table(is.na(data_rel$relationship_status)) # NAs
```

##### Relationship length 
```{r}
table(data_rel$relationship_length)
range(data_rel$relationship_length, na.rm = T) # range
table(is.na(data_rel$relationship_length)) # NAs
# histogram
hist(data_rel$relationship_length)

# mean, sd
mean(data_rel$relationship_length, na.rm = T)
sd(data_rel$relationship_length, na.rm = T)
```

#### Outcomes: Relationship options
```{r}
# mean
data_rel %>%
  select(interest_hookups,
         interest_nonsexrel,
         interest_monrel,
         interest_nonmonrel,
         interest_altrel,
         interest_single,
         interest_parent) %>% 
  colMeans(na.rm = T) 

# standard deviation
round(apply(data_rel %>% select(interest_hookups,
                                 interest_nonsexrel,
                                 interest_monrel,
                                 interest_nonmonrel,
                                 interest_altrel,
                                 interest_parent),2, sd, na.rm = T),2)

# check for NAs
table(is.na(data_rel$interest_hookups))
table(is.na(data_rel$interest_nonsexrel))
table(is.na(data_rel$interest_monrel))
table(is.na(data_rel$interest_nonmonrel))
table(is.na(data_rel$interest_altrel))
table(is.na(data_rel$interest_single))
table(is.na(data_rel$interest_parent))
```

#### Zero-order correlations
```{r}
correlations_psm_rel = data_rel %>%
  select(interest_hookups,
         interest_nonsexrel,
         interest_monrel,
         interest_nonmonrel,
         interest_altrel,
         interest_single,
         interest_parent,
         )


# correlations_table_psm_rel = apa.cor.table(correlations_psm_rel, filename = "Table1.doc", table.number = 1)
# correlations_table_psm_rel
```



### Descriptives by sexual orientation
#### Demographic data
```{r}
# quick overview 
describe.by(data_rel, data_rel$sexual_orientation)

# split data set by sexual orientation
asexuals_rel = data_rel %>% filter(sexual_orientation == "Asexual")
heteros_rel = data_rel %>% filter(sexual_orientation == "Straight/Heterosexual")
```

##### Country
```{r}
# for asexuals
sort(table(asexuals_rel$country), decreasing = T) # absolute numbers
sort(round(table(asexuals_rel$country)/sum(table(asexuals_rel$country)),4)*100, decreasing = T) # in percent
  
# for heteros_relexuals
sort(table(heteros_rel$country), decreasing = T) # absolute numbers
sort(round(table(heteros_rel$country)/sum(table(heteros_rel$country)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_rel_rel$country))
table(is.na(heteros_rel$country))
```

##### Language
```{r}
# for asexuals_rel_rel
sort(table(asexuals_rel$language), decreasing = T) # absolute numbers
sort(round(table(asexuals_rel$language)/sum(table(asexuals_rel$language)),4)*100, decreasing = T) # in percent

# for heterosexuals
sort(table(heteros_rel$language), decreasing = T) # absolute numbers
sort(round(table(heteros_rel$language)/sum(table(heteros_rel$language)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_rel$language))
table(is.na(heteros_rel$language))

```

##### Age
```{r}
# mean, sd, min, max
data_rel %>%
  group_by(sexual_orientation) %>%
  summarise(mean(age, na.rm = T), 
            min(age, na.rm = T), 
            max(age, na.rm = T),
            sd(age, na.rm = T))


# Histogram by group 
ggplot(data_rel, aes(x = age, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")


# check NAs
data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(age)))
```

##### Relationship status
```{r}
# for asexuals_rel
sort(table(asexuals_rel$relationship_status), decreasing = T) # absolute numbers
sort(round(table(asexuals_rel$relationship_status)/sum(table(asexuals_rel$relationship_status)),4)*100, decreasing = T) # in percent

# for heterosexuals
sort(table(heteros_rel$relationship_status), decreasing = T) # absolute numbers
sort(round(table(heteros_rel$relationship_status)/sum(table(heteros_rel$relationship_status)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_rel$relationship_status))
table(is.na(heteros_rel$relationship_status))
```

##### Relationship length 
```{r}
# mean, sd, min, max
data_rel %>%
  group_by(sexual_orientation) %>%
  summarise(mean(relationship_length, na.rm = T), 
            min(relationship_length, na.rm = T), 
            max(relationship_length, na.rm = T),
            sd(relationship_length, na.rm = T))


# Histogram by group 
ggplot(data_rel, aes(x = relationship_length, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")


# check NAs
data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(relationship_length)))
```

#### Outcomes: Relationship options
```{r}
# mean
data_rel %>% group_by(sexual_orientation) %>% 
  summarise_at(c("interest_hookups", "interest_nonsexrel", "interest_monrel",
                 "interest_nonmonrel","interest_altrel", "interest_single", 
                 "interest_parent"), mean, na.rm = T)


# standard deviation
data_rel %>% group_by(sexual_orientation) %>% 
  summarise_at(c("interest_hookups", "interest_nonsexrel", "interest_monrel",
                 "interest_nonmonrel","interest_altrel", "interest_single", 
                 "interest_parent"), sd, na.rm = T)
# min
data_rel %>% group_by(sexual_orientation) %>% 
  summarise_at(c("interest_hookups", "interest_nonsexrel", "interest_monrel",
                 "interest_nonmonrel","interest_altrel", "interest_single", 
                 "interest_parent"), min, na.rm = T)
# max
data_rel %>% group_by(sexual_orientation) %>% 
  summarise_at(c("interest_hookups", "interest_nonsexrel", "interest_monrel",
                 "interest_nonmonrel","interest_altrel", "interest_single", 
                 "interest_parent"), max, na.rm = T)

# check NAs
data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_hookups)))

data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_nonsexrel)))

data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_monrel)))

data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_nonmonrel)))

data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_altrel)))

data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_single)))

data_rel %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(interest_parent)))


# Total number per variable by sexual orientation
data_rel %>% group_by(sexual_orientation) %>% 
  summarise_at(c("interest_hookups", "interest_nonsexrel", "interest_monrel",
                 "interest_nonmonrel","interest_altrel", "interest_single", "interest_parent"), sum, na.rm = T)


# histogram
# sexual, non-romantic relationship
ggplot(data_rel, aes(x = interest_hookups, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# non-sexual, romantic relationship
ggplot(data_rel, aes(x = interest_nonsexrel, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# monogamous relationship
ggplot(data_rel, aes(x = interest_monrel, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# non-monogamous relationship
ggplot(data_rel, aes(x = interest_nonmonrel, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# alternative committed relationship
ggplot(data_rel, aes(x = interest_altrel, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# single
ggplot(data_rel, aes(x = interest_single, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# parent
ggplot(data_rel, aes(x = interest_parent, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")
```


## 2. Partner preferences
### Descriptives for whole sample
#### Demographic data
##### Sexual orientation
```{r}
table(data_prefs$sexual_orientation) # sexual orientation in absolute numbers
round(table(data_prefs$sexual_orientation)/sum(table(data_prefs$sexual_orientation)),4)*100 # sexual orientation in percent
table(is.na(data_prefs$sexual_orientation)) # no NAs 
```

##### Country
```{r}
table(data_prefs$country) # country in absolute numbers
round(table(data_prefs$country)/sum(table(data_prefs$country)),4)*100 # country in percent
table(is.na(data_prefs$country)) # no NAs 
```

##### Language
Chinese, Danish, English, French, German, Japanese, Portuguese, Russian, Spanish, Italian
```{r Language}
table(data_prefs$language) # language in absolute numbers
round(table(data_prefs$country)/sum(table(data_prefs$country)),4)*100 # country in percent
table(is.na(data_prefs$language)) #no NAs
```

##### Age
```{r}
table(data_prefs$age)
range(data_prefs$age, na.rm = T) # range
table(is.na(data_prefs$age)) # NAs

# histogram 
hist(data_prefs$age)

# mean, sd
mean(data_prefs$age, na.rm = T)
sd(data_prefs$age, na.rm = T)
```

##### Sex 
```{r Sex}
table(data_prefs$sex) # in absolute numbers
round(table(data_prefs$sex)/sum(table(data_prefs$sex)),4)*100 # in percent
table(is.na(data_prefs$sex))
```

##### Relationship status
```{r}
table(data_prefs$relationship_status) # in absolute numbers
round(table(data_prefs$relationship_status)/sum(table(data_prefs$relationship_status)),4)*100 # in percent
table(is.na(data_prefs$relationship_status)) # NAs
```

##### Relationship length 
```{r}
table(data_prefs$relationship_length)
range(data_prefs$relationship_length, na.rm = T) # range
table(is.na(data_prefs$relationship_length)) # NAs
# histogram
hist(data_prefs$relationship_length)

# mean, sd
mean(data_prefs$relationship_length, na.rm = T)
sd(data_prefs$relationship_length, na.rm = T)
```


#### Outcomes: partner preferences
```{r}
# mean
data_prefs %>% select(pref_imp_ks,
                     pref_imp_att,
                     pref_imp_fs,
                     pref_imp_ca,
                     pref_imp_ei,
                     pref_imp_sexually_experienced) %>% 
              colMeans(na.rm = T) 

# standard deviations
round(apply(data_prefs %>% select(pref_imp_ks,
                                 pref_imp_att,
                                 pref_imp_fs,
                                 pref_imp_ca,
                                 pref_imp_ei,
                                 pref_imp_sexually_experienced),2, sd, na.rm = T),2)

# check for NAs
table(is.na(data_prefs$pref_imp_ks))
table(is.na(data_prefs$pref_imp_att))
table(is.na(data_prefs$pref_imp_fs))
table(is.na(data_prefs$pref_imp_ca))
table(is.na(data_prefs$pref_imp_ei))
table(is.na(data_prefs$pref_imp_sexually_experienced))
```


#### Zero-order correlations
```{r}
correlations_psm_prefs = data_prefs %>%
  select(pref_imp_ca,
         pref_imp_att,
         pref_imp_sexually_experienced,
         pref_imp_ks,
         pref_imp_fs,
         pref_imp_ei
        )


# correlations_table_psm_prefs = apa.cor.table(correlations_psm_prefs, filename = "Table2.doc", table.number = 2)
# correlations_table_psm_prefs
```
### Descriptives by sexual orientation
#### Demographic data
```{r}
# quick overview 
describe.by(data_prefs, data_prefs$sexual_orientation)

# split data set by sexual orientation
asexuals_prefs = data_prefs %>% filter(sexual_orientation == "Asexual")
heteros_prefs = data_prefs %>% filter(sexual_orientation == "Straight/Heterosexual")
```

##### Country
```{r}
# for asexuals
sort(table(asexuals_prefs$country), decreasing = T) # absolute numbers
sort(round(table(asexuals_prefs$country)/sum(table(asexuals_prefs$country)),4)*100, decreasing = T) # in percent
  
# for heterosexuals
sort(table(heteros_prefs$country), decreasing = T) # absolute numbers
sort(round(table(heteros_prefs$country)/sum(table(heteros_prefs$country)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_prefs_rel$country))
table(is.na(heteros_prefs$country))
```

##### Language
```{r}
# for asexuals
sort(table(asexuals_prefs$language), decreasing = T) # absolute numbers
sort(round(table(asexuals_prefs$language)/sum(table(asexuals_prefs$language)),4)*100, decreasing = T) # in percent

# for heterosexuals
sort(table(heteros_prefs$language), decreasing = T) # absolute numbers
sort(round(table(heteros_prefs$language)/sum(table(heteros_prefs$language)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_prefs$language))
table(is.na(heteros_prefs$language))

```

##### Age
```{r}
# mean, sd, min, max
data_prefs %>%
  group_by(sexual_orientation) %>%
  summarise(mean(age, na.rm = T), 
            min(age, na.rm = T), 
            max(age, na.rm = T),
            sd(age, na.rm = T))


# Histogram by group 
ggplot(data_prefs, aes(x = age, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")


# check NAs
data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(age)))
```

##### Relationship status
```{r}
# for asexuals_prefs
sort(table(asexuals_prefs$relationship_status), decreasing = T) # absolute numbers
sort(round(table(asexuals_prefs$relationship_status)/sum(table(asexuals_prefs$relationship_status)),4)*100, decreasing = T) # in percent

# for heterosexuals
sort(table(heteros_prefs$relationship_status), decreasing = T) # absolute numbers
sort(round(table(heteros_prefs$relationship_status)/sum(table(heteros_prefs$relationship_status)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_prefs$relationship_status))
table(is.na(heteros_prefs$relationship_status))
```

##### Relationship length 
```{r}
# mean, sd, min, max
data_prefs %>%
  group_by(sexual_orientation) %>%
  summarise(mean(relationship_length, na.rm = T), 
            min(relationship_length, na.rm = T), 
            max(relationship_length, na.rm = T),
            sd(relationship_length, na.rm = T))


# Histogram by group 
ggplot(data_prefs, aes(x = relationship_length, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")


# check NAs
data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(relationship_length)))
```

#### Outcomes: partner preferences
```{r}
# mean
data_prefs %>% group_by(sexual_orientation) %>% 
  summarise_at(c("pref_imp_ks",
                 "pref_imp_att",
                 "pref_imp_fs",
                 "pref_imp_ca",
                 "pref_imp_ei",
                 "pref_imp_sexually_experienced"), mean, na.rm = T)


# standard deviation
data_prefs %>% group_by(sexual_orientation) %>% 
  summarise_at(c("pref_imp_ks",
                 "pref_imp_att",
                 "pref_imp_fs",
                 "pref_imp_ca",
                 "pref_imp_ei",
                 "pref_imp_sexually_experienced"), sd, na.rm = T)
# min
data_prefs %>% group_by(sexual_orientation) %>% 
  summarise_at(c("pref_imp_ks",
                 "pref_imp_att",
                 "pref_imp_fs",
                 "pref_imp_ca",
                 "pref_imp_ei",
                 "pref_imp_sexually_experienced"), min, na.rm = T)
# max
data_prefs %>% group_by(sexual_orientation) %>% 
  summarise_at(c("pref_imp_ks",
                 "pref_imp_att",
                 "pref_imp_fs",
                 "pref_imp_ca",
                 "pref_imp_ei",
                 "pref_imp_sexually_experienced"), max, na.rm = T)


# check NAs
data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(pref_imp_ks)))

data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(pref_imp_att)))

data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(pref_imp_fs)))

data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(pref_imp_ca)))

data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(pref_imp_ei)))

data_prefs %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(pref_imp_sexually_experienced)))




# Total number of observations per variable by sexual orientation
data_prefs %>% group_by(sexual_orientation) %>% 
  summarise_at(c("pref_imp_ks",
                 "pref_imp_att",
                 "pref_imp_fs",
                 "pref_imp_ca",
                 "pref_imp_ei",
                 "pref_imp_sexually_experienced"), sum, na.rm = T)

# histogram
# kind-supportive
ggplot(data_prefs, aes(x = pref_imp_ks, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# attractive
ggplot(data_prefs, aes(x = pref_imp_att, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# financially secure-successful
ggplot(data_prefs, aes(x = pref_imp_fs, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# confident-assertive
ggplot(data_prefs, aes(x = pref_imp_ca, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# educated-intelligent
ggplot(data_prefs, aes(x = pref_imp_ei, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# sexually experienced
ggplot(data_prefs, aes(x = pref_imp_sexually_experienced, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")
```


## 3. Self-ratings
### Descriptives for whole sample
#### Demographic data
##### Sexual orientation
```{r}
table(data_self$sexual_orientation) # sexual orientation in absolute numbers
round(table(data_self$sexual_orientation)/sum(table(data_self$sexual_orientation)),4)*100 # sexual orientation in percent
table(is.na(data_self$sexual_orientation)) # no NAs 
```

##### Country
```{r}
table(data_self$country) # country in absolute numbers
round(table(data_self$country)/sum(table(data_self$country)),4)*100 # country in percent
table(is.na(data_self$country)) # no NAs 
```

##### Language
Chinese, Danish, English, French, German, Japanese, Portuguese, Russian, Spanish, Italian
```{r Language}
table(data_self$language) # language in absolute numbers
round(table(data_self$country)/sum(table(data_self$country)),4)*100 # country in percent
table(is.na(data_self$language)) #no NAs
```

##### Age
```{r}
table(data_self$age)
range(data_self$age, na.rm = T) # range
table(is.na(data_self$age)) # NAs

# histogram 
hist(data_self$age)

# mean, sd
mean(data_self$age, na.rm = T)
sd(data_self$age, na.rm = T)
```

##### Sex 
```{r Sex}
table(data_self$sex) # in absolute numbers
round(table(data_self$sex)/sum(table(data_self$sex)),4)*100 # in percent
table(is.na(data_self$sex))
```

##### Relationship status
```{r}
table(data_self$relationship_status) # in absolute numbers
round(table(data_self$relationship_status)/sum(table(data_self$relationship_status)),4)*100 # in percent
table(is.na(data_self$relationship_status)) # NAs
```

##### Relationship length 
```{r}
table(data_self$relationship_length)
range(data_self$relationship_length, na.rm = T) # range
table(is.na(data_self$relationship_length)) # NAs
# histogram
hist(data_self$relationship_length)

# mean, sd
mean(data_self$relationship_length, na.rm = T)
sd(data_self$relationship_length, na.rm = T)
```

#### Outcomes: self-ratings
```{r}
# mean
data_self %>% select(self_ks,
                     self_att,
                     self_fs,
                     self_ca,
                     self_ei,
                     self_sexually_experienced) %>% 
              colMeans(na.rm = T) 


# standard deviation
round(apply(data_self %>% select(self_ks,
                                 self_att,
                                 self_fs,
                                 self_ca,
                                 self_ei,
                                 self_sexually_experienced),2, sd, na.rm = T),2)


# check for NAS
table(is.na(data_self$self_ks))
table(is.na(data_self$self_att))
table(is.na(data_self$self_fs))
table(is.na(data_self$self_ca))
table(is.na(data_self$self_ei))
table(is.na(data_self$self_sexually_experienced))
```

#### Zero-order correlations
```{r}
correlations_psm_self = data_self %>%
  select(self_ca,
         self_att,
         self_sexually_experienced,
         self_ks,
         self_fs,
         self_ei)

# correlations_table_psm_self = apa.cor.table(correlations_psm_self, filename = "Table3.doc", table.number = 3)
# correlations_table_psm_self
```

### Descriptives by sexual orientation
#### Demographic data
```{r}
# quick overview 
describe.by(data_self, data_self$sexual_orientation)

# split data set by sexual orientation
asexuals_self = data_self %>% filter(sexual_orientation == "Asexual")
heteros_self = data_self %>% filter(sexual_orientation == "Straight/Heterosexual")
```

##### Country
```{r}
# for asexuals
sort(table(asexuals_self$country), decreasing = T) # absolute numbers
sort(round(table(asexuals_self$country)/sum(table(asexuals_self$country)),4)*100, decreasing = T) # in percent
  
# for heterosexuals
sort(table(heteros_self$country), decreasing = T) # absolute numbers
sort(round(table(heteros_self$country)/sum(table(heteros_self$country)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_self$country))
table(is.na(heteros_self$country))
```

##### Language
```{r}
# for asexuals
sort(table(asexuals_self$language), decreasing = T) # absolute numbers
sort(round(table(asexuals_self$language)/sum(table(asexuals_self$language)),4)*100, decreasing = T) # in percent

# for heterosexuals
sort(table(heteros_self$language), decreasing = T) # absolute numbers
sort(round(table(heteros_self$language)/sum(table(heteros_self$language)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_self$language))
table(is.na(heteros_self$language))

```

##### Age
```{r}
# mean, sd, min, max
data_self %>%
  group_by(sexual_orientation) %>%
  summarise(mean(age, na.rm = T), 
            min(age, na.rm = T), 
            max(age, na.rm = T),
            sd(age, na.rm = T))


# Histogram by group 
ggplot(data_self, aes(x = age, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")


# check NAs
data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(age)))
```

##### Relationship status
```{r}
# for asexuals_self
sort(table(asexuals_self$relationship_status), decreasing = T) # absolute numbers
sort(round(table(asexuals_self$relationship_status)/sum(table(asexuals_self$relationship_status)),4)*100, decreasing = T) # in percent

# for heterosexuals
sort(table(heteros_self$relationship_status), decreasing = T) # absolute numbers
sort(round(table(heteros_self$relationship_status)/sum(table(heteros_self$relationship_status)),4)*100, decreasing = T) # in percent


# check for NAs
table(is.na(asexuals_self$relationship_status))
table(is.na(heteros_self$relationship_status))
```

##### Relationship length 
```{r}
# mean, sd, min, max
data_self %>%
  group_by(sexual_orientation) %>%
  summarise(mean(relationship_length, na.rm = T), 
            min(relationship_length, na.rm = T), 
            max(relationship_length, na.rm = T),
            sd(relationship_length, na.rm = T))


# Histogram by group 
ggplot(data_self, aes(x = relationship_length, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")


# check NAs
data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(relationship_length)))
```

#### Outcomes: self-ratings
```{r}
# mean
data_self %>% group_by(sexual_orientation) %>% 
  summarise_at(c("self_ks",
                 "self_att",
                 "self_fs",
                 "self_ca",
                 "self_ei",
                 "self_sexually_experienced"), mean, na.rm = T)


# standard deviation
data_self %>% group_by(sexual_orientation) %>% 
  summarise_at(c("self_ks",
                 "self_att",
                 "self_fs",
                 "self_ca",
                 "self_ei",
                 "self_sexually_experienced"), sd, na.rm = T)
# min
data_self %>% group_by(sexual_orientation) %>% 
  summarise_at(c("self_ks",
                 "self_att",
                 "self_fs",
                 "self_ca",
                 "self_ei",
                 "self_sexually_experienced"), min, na.rm = T)
# max
data_self %>% group_by(sexual_orientation) %>% 
  summarise_at(c("self_ks",
                 "self_att",
                 "self_fs",
                 "self_ca",
                 "self_ei",
                 "self_sexually_experienced"), max, na.rm = T)

# check NAs
data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(self_ks)))

data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(self_att)))

data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(self_fs)))

data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(self_ca)))

data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(self_ei)))

data_self %>% 
  group_by(sexual_orientation) %>% 
  summarise(sum(is.na(self_sexually_experienced)))


# Total number of observations per variable by sexual orientation
data_self %>% group_by(sexual_orientation) %>% 
  summarise_at(c("self_ks",
                 "self_att",
                 "self_fs",
                 "self_ca",
                 "self_ei",
                 "self_sexually_experienced"), sum, na.rm = T)

# histograms
# kind-supportive
ggplot(data_self, aes(x = self_ks, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# attractive
ggplot(data_self, aes(x = self_att, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# financially secure-successful
ggplot(data_self, aes(x = self_fs, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# confident-assertive
ggplot(data_self, aes(x = self_ca, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# educated-intelligent
ggplot(data_self, aes(x = self_ei, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

# sexually experienced
ggplot(data_self, aes(x = self_sexually_experienced, fill = sexual_orientation)) + 
  geom_histogram(position = "dodge")

```



