---
title: "06_analyses"
output: html_document
date: '2022-04-19'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analyses

## Library
```{r}
library(dplyr)
library(formr)
library(ggplot2)
library(psych)
library(effsize)
```

## Load data
```{r}
data_rel = read.csv(file = "data/data_rel.csv")[,-1]
data_prefs = read.csv(file = "data/data_prefs.csv")[,-1]
data_self = read.csv(file = "data/data_self.csv")[,-1]
```

## sort data by subclass number within sexual_orientation
```{r}
data_rel = data_rel %>% 
        group_by(sexual_orientation) %>%
        arrange(subclass, .by_group = TRUE)

data_prefs = data_prefs %>% 
        group_by(sexual_orientation) %>%
        arrange(subclass, .by_group = TRUE)

data_self = data_self %>% 
        group_by(sexual_orientation) %>%
        arrange(subclass, .by_group = TRUE)
```

## 1. Relationship options
### interest non-sexual relationships
```{r}
t.test(interest_nonsexrel ~ sexual_orientation, 
       data = data_rel,
       alternative = "greater",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_nonsexrel ~ sexual_orientation, data = data_rel, paired = T)
```

### interest sexual relationships
```{r}
t.test(interest_hookups ~ sexual_orientation, 
       data = data_rel,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_hookups ~ sexual_orientation, data = data_rel, paired = T)
```

### interest non-monogamous relationships
```{r}
t.test(interest_nonmonrel ~ sexual_orientation, 
       data = data_rel,
       alternative = "greater",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_nonmonrel ~ sexual_orientation, data = data_rel, paired = T)
```

### interest alternativ committed relationships
```{r}
t.test(interest_altrel ~ sexual_orientation, 
       data = data_rel,
       alternative = "greater",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_altrel ~ sexual_orientation, data = data_rel, paired = T)
```

### interest single
```{r}
t.test(interest_single ~ sexual_orientation, 
       data = data_rel,
       alternative = "greater",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_single ~ sexual_orientation, data = data_rel, paired = T)
```

## Exploratory analyses
### interest monogamous relationships
```{r}
t.test(interest_monrel ~ sexual_orientation, 
       data = data_rel,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_monrel ~ sexual_orientation, data = data_rel, paired = T)
```

### interest parent 
```{r}
t.test(interest_parent ~ sexual_orientation, 
       data = data_rel,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(interest_parent ~ sexual_orientation, data = data_rel, paired = T)
```


## 2. Partner preferences
### confident-assertive
```{r}
t.test(pref_imp_ca ~ sexual_orientation, 
       data = data_prefs,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(pref_imp_ca ~ sexual_orientation, data = data_prefs, paired = T)
```

### attractive
```{r}
t.test(pref_imp_att ~ sexual_orientation, 
       data = data_prefs,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(pref_imp_att ~ sexual_orientation, data = data_prefs, paired = T)
```

### sexually experienced
```{r}
t.test(pref_imp_sexually_experienced ~ sexual_orientation, 
       data = data_prefs,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(pref_imp_sexually_experienced ~ sexual_orientation, data = data_prefs, paired = T)
```

## Exploratory analyses
### kind-supportive
```{r}
t.test(pref_imp_ks ~ sexual_orientation, 
       data = data_prefs,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(pref_imp_ks ~ sexual_orientation, data = data_prefs, paired = T)
```


### financially-secure/successfull
```{r}
t.test(pref_imp_fs ~ sexual_orientation, 
       data = data_prefs,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(pref_imp_fs ~ sexual_orientation, data = data_prefs, paired = T)
```


### educated-intelligent
```{r}
t.test(pref_imp_ei ~ sexual_orientation, 
       data = data_prefs,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(pref_imp_ei ~ sexual_orientation, data = data_prefs, paired = T)
```


## 3. Self-ratings
### confident-assertive
```{r}
t.test(self_ca ~ sexual_orientation, 
       data = data_self,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(self_ca ~ sexual_orientation, data = data_self, paired = T)
```

### attractive
```{r}
t.test(self_att ~ sexual_orientation, 
       data = data_self,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(self_att ~ sexual_orientation, data = data_self, paired = T)
```

### sexually experienced
```{r}
t.test(self_sexually_experienced ~ sexual_orientation, 
       data = data_self,
       alternative = "less",
       paired = TRUE)


# effect size
effsize::cohen.d(self_sexually_experienced ~ sexual_orientation, data = data_self, paired = T)
```

## Exploratory analyses
### kind-supportive
```{r}
t.test(self_ks ~ sexual_orientation, 
       data = data_self,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(self_ks ~ sexual_orientation, data = data_self, paired = T)
```


### financially-secure/successfull
```{r}
t.test(self_fs ~ sexual_orientation, 
       data = data_self,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(self_fs ~ sexual_orientation, data = data_self, paired = T)
```

### educated-intelligent
```{r}
t.test(self_ei ~ sexual_orientation, 
       data = data_self,
       alternative = "two.sided",
       paired = TRUE)


# effect size
effsize::cohen.d(self_ei ~ sexual_orientation, data = data_self, paired = T)
```

