---
title: "Number of Lifetime Sexual Partners"
output: 
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
    code_folding: 'show'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

## Library
```{r}
library(ggplot2)
library(dplyr)
library(effsize)
```

## Load data
```{r}
# load data_prefs and data_self
data_rel = read.csv(file = "data/data_rel.csv")[,-1]
data_prefs = read.csv(file = "data/data_prefs.csv")[,-1]
data_self = read.csv(file = "data/data_self.csv")[,-1]

# load data with lifetime sexual partners variable
fulldata_selected_plus_sexual_partner_variable = read.csv(file = "data/fulldata_selected_plus_sexual_partner_variable.csv")[,-1]
names(fulldata_selected_plus_sexual_partner_variable)
sexual_partner = fulldata_selected_plus_sexual_partner_variable %>% select("total_sex_partners", "total_sex_partners2")
```


Add id variable and add lifetime sexual partner variable to data sets
```{r}
# add id variable to sexual partner data set
sexual_partner$id = 1:94738

# add variables to data
data_rel_plus_sexual_partner_variable = left_join(data_rel, sexual_partner)
data_prefs_plus_sexual_partner_variable = left_join(data_prefs, sexual_partner) # joined by id variable
data_self_plus_sexual_partner_variable = left_join(data_self, sexual_partner) # joined by id variable
```


## Partner preferences: look at sexual partners variables
```{r}
# mean
data_prefs_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), mean, na.rm = T)

# sd
data_prefs_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), sd, na.rm = T)

# min
data_prefs_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), min, na.rm = T)

# max
data_prefs_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), max, na.rm = T)

# range
data_prefs_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), range, na.rm = T)

# median
data_prefs_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), median, na.rm = T)

# counts
table(data_prefs_plus_sexual_partner_variable$total_sex_partners)
table(data_prefs_plus_sexual_partner_variable$total_sex_partners2)

# correlation
cor.test(data_prefs_plus_sexual_partner_variable$total_sex_partners, data_prefs_plus_sexual_partner_variable$total_sex_partners2, method = "pearson", na.rm = T)
```
Both variables are highly correlated (r = 0.99) - as expected. total_sex_partners_2 will be used for the following analysis.


### Correlation between number of total sex partners and preference for a sexually experienced partner
```{r}
cor.test(data_prefs_plus_sexual_partner_variable$total_sex_partners2, data_prefs_plus_sexual_partner_variable$pref_imp_sexually_experienced, method = "pearson", na.rm = T)
```
r = 0.26

### t-test difference between asexuals and heterosexuals in total number of sex partners
```{r}
t.test(total_sex_partners2 ~ sexual_orientation, data = data_prefs_plus_sexual_partner_variable,
       alternative = "two.sided",
       paired = F)

effsize::cohen.d(total_sex_partners2 ~ sexual_orientation, data = data_prefs_plus_sexual_partner_variable,
       paired = F)
```


## Self-ratings: look at sexual partners variables
```{r}
# mean
data_self_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), mean, na.rm = T)

# sd
data_self_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), sd, na.rm = T)

# min
data_self_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), min, na.rm = T)

# max
data_self_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), max, na.rm = T)

# range
data_self_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), range, na.rm = T)

# median
data_self_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), median, na.rm = T)

# counts
table(data_self_plus_sexual_partner_variable$total_sex_partners)
table(data_self_plus_sexual_partner_variable$total_sex_partners2)

# correlation
cor.test(data_self_plus_sexual_partner_variable$total_sex_partners, data_self_plus_sexual_partner_variable$total_sex_partners2, method = "pearson", na.rm = T)
```
Both variables are highly correlated (r = 0.99).

### Correlation between total number of sex partners and being sexually experienced 
```{r}
cor.test(data_self_plus_sexual_partner_variable$total_sex_partners2, data_self_plus_sexual_partner_variable$self_sexually_experienced, method = "pearson", na.rm = T)
```

### t-test difference between asexuals and heterosexuals in total number of sex partners
```{r}
t.test(total_sex_partners2 ~ sexual_orientation, data = data_self_plus_sexual_partner_variable,
       alternative = "two.sided",
       paired = F)

effsize::cohen.d(total_sex_partners2 ~ sexual_orientation, data = data_self_plus_sexual_partner_variable,
       paired = F)
```

### Plot total number of sex partners and sexual experience againts each other
```{r}
b <- ggplot(data_self_plus_sexual_partner_variable, aes(x = total_sex_partners2, y = self_sexually_experienced))
# Scatter plot with regression line
b + geom_point()+
  geom_smooth(method = "lm") 
```

## Relationship options: look at sexual partners variables
```{r}
# mean
data_rel_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), mean, na.rm = T)

# sd
data_rel_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), sd, na.rm = T)

# min
data_rel_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), min, na.rm = T)

# max
data_rel_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), max, na.rm = T)

# range
data_rel_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), range, na.rm = T)

# median
data_rel_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), median, na.rm = T)

# counts
table(data_rel_plus_sexual_partner_variable$total_sex_partners)
table(data_rel_plus_sexual_partner_variable$total_sex_partners2)
```



## Lifetime sexual partners in unmatched heterosexuals sample
### Load data
```{r}
data_prefs_unmatched = read.csv(file = "data/data_prefs_unmatched.csv")[,-1]
data_self_unmatched = read.csv(file = "data/data_prefs_unmatched.csv")[,-1]

# add sex partner variable to data
data_prefs_unmatched_plus_sexual_partner_variable = left_join(data_prefs_unmatched, sexual_partner)
data_self_unmatched_plus_sexual_partner_variable = left_join(data_self_unmatched, sexual_partner)
```

### Partner preferences
#### Total number of sex partners
```{r}
# mean
data_prefs_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), mean, na.rm = T)

# sd
data_prefs_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), sd, na.rm = T)

# min
data_prefs_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), min, na.rm = T)

# max
data_prefs_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), max, na.rm = T)

# range
data_prefs_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), range, na.rm = T)

# median
data_prefs_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), median, na.rm = T)

# counts
table(data_prefs_unmatched_plus_sexual_partner_variable$total_sex_partners)
table(data_prefs_unmatched_plus_sexual_partner_variable$total_sex_partners2)
```
Using variable total_sex_partners as total_sex_partners2 seems to have unreasonably high values.
Mean number of lifetime sexual partners in unmatched heterosexual sample is 6.23. 

### Self-ratings
#### Total number of sex partners
```{r}
# mean
data_self_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), mean, na.rm = T)

# sd
data_self_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), sd, na.rm = T)

# min
data_self_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), min, na.rm = T)

# max
data_self_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), max, na.rm = T)

# range
data_self_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), range, na.rm = T)

# median
data_self_unmatched_plus_sexual_partner_variable %>% group_by(sexual_orientation) %>%
  summarise_at(c("total_sex_partners", "total_sex_partners2"), median, na.rm = T)

# counts
table(data_self_unmatched_plus_sexual_partner_variable$total_sex_partners)
table(data_self_unmatched_plus_sexual_partner_variable$total_sex_partners2)
```
Using variable total_sex_partners as total_sex_partners2 seems to have unreasonably high values.
Mean number of lifetime sexual partners in unmatched heterosexual sample is 6.23. 

