---
title: "06_forest_plot"
output: html_document
date: '2022-06-07'
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
```{r}
library(dplyr)
library(formr)
library(ggplot2)
library(psych)
library(effsize)
library(forestplot)
```


# Create forest plot for each outcome section with effect sizes and 95% CIs
## Preferred relationship options
```{r}
base_data_rel <- tibble(mean  = c(-0.67, 1.12, -0.46, 0.20, 0.57, 0.61, -0.77), 
                    lower = c(-0.83, 0.93, -0.61, 0.05, 0.41, 0.45, -0.94),
                    upper = c(-0.51, 1.32, -0.31, 0.35, 0.73, 0.76, -0.61),
                    Preferred_relationship_options = c("Sexual, non-romantic", "Non-sexual, romantic", "Monogamous", "Non-monogamous", "Alternative committed", "Being non-partnered", "Becoming a parent"),
                    d = c("-0.67", "1.12", "-0.46", "0.20", "0.57", "0.61", "-0.77"))


header_rel <- tibble(Preferred_relationship_options = c("", "Outcome"),
                d = c("", "d"),
                 summary = TRUE)

preferred_relationship_options <- bind_rows(header_rel,
                                base_data_rel)



plot_preferred_relationship_options = preferred_relationship_options  %>% 
  forestplot(labeltext = c(Preferred_relationship_options, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
              xticks = c(-1.5,-1, -0.5, -0.26,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Preferred Relationship Options ("*bolditalic(N)~"= 646)")),
             graphwidth = unit(150, "mm"),
           colgap = unit(25, "mm")
             )

plot_preferred_relationship_options
```


## Partner preferences
```{r}
base_data_prefs <- tibble(mean  = c(-0.37, -0.52, -0.66, -0.16, -0.21, 0.01), 
                    lower = c(-0.51, -0.66, -0.81, -0.30, -0.35, -0.12),
                    upper = c(-0.24, -0.37, -0.51, -0.02, -0.08, 0.15),
                    Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.37", "-0.52", "-0.66", "-0.16", "-0.21", "0.01"))


header_prefs <- tibble(Partner_preferences = c("", "Outcome"),
                d = c("", "d"),
                 summary = TRUE)


partner_preferences_prefs <- bind_rows(header_prefs,
                                base_data_prefs)



plot_partner_preferences = partner_preferences_prefs %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-2,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5,-1, -0.5, -0.26,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab = gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Ideal Long-Term Partner Preferences ("*bolditalic(N)~"= 780)")),
             graphwidth = unit(150, "mm"),
             colgap = unit(25, "mm")
             )

plot_partner_preferences
```



## Self-ratings
```{r}
base_data_self <- tibble(mean  = c(-0.43, -0.49, -0.65, -0.40, -0.45, -0.17), 
                    lower = c(-0.57, -0.63, -0.79, -0.54, -0.60, -0.31),
                    upper = c(-0.29, -0.34, -0.52, -0.25, -0.31, -0.04),
                    self_ratings = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.43", "-0.49", "-0.65", "-0.40", "-0.45", "-0.17"))

header_self <- tibble(self_ratings = c("", "Outcome"),
                d = c("", "d"),
                 summary = TRUE)

self_ratings <- bind_rows(header_self,
                          base_data_self)

plot_self_ratings = self_ratings %>% 
  forestplot(labeltext = c(self_ratings, d), 
             graph.pos = 3,
              clip = c(-2,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5,-1, -0.5, -0.26,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Self-Ratings ("~bolditalic(N)~"= 772)")),
             graphwidth = unit(150, "mm"))

plot_self_ratings
```

```{r}
library(ggplotify)
library(patchwork)

p1 <- grid2grob(print(plot_preferred_relationship_options))
p2 <- grid2grob(print(plot_partner_preferences))
p3 <- grid2grob(print(plot_self_ratings))
p_all <- wrap_elements(p1) / wrap_elements(p2) /wrap_elements((p3))
p_all
?wrap_elements

```


# Forest plots for robustness analyses
## Preferred relationship options
```{r}
base_data_rel_robust <- tibble(mean  = c(-0.61, 1.12, -0.46, 0.29, 0.61, 0.66, -0.72), 
                               lower = c(-0.76, 0.94, -0.61, 0.15, 0.46, 0.51, -0.87),
                               upper = c(-0.45, 1.29, -0.31, 0.43, 0.76, 0.80, -0.56),
                               Preferred_relationship_options = c("Sexual, non-romantic", "Non-sexual, romantic", "Monogamous", "Non-monogamous", "Alternative committed", "Being non-partnered", "Becoming a parent"),
                               d = c("-0.61", "1.12", "-0.46", "0.29", "0.61", "0.66", "-0.72"))


header_rel_robust <- tibble(Preferred_relationship_options = c("", "Outcome"),
                d = c("", "d"),
                 summary = TRUE)


preferred_relationship_options_robust <- bind_rows(header_rel_robust,
                                base_data_rel_robust)



plot_preferred_relationship_options_robust = preferred_relationship_options_robust  %>% 
  forestplot(labeltext = c(Preferred_relationship_options, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
              xticks = c(-1.5,-1, -0.5, -0.26,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Preferred Relationship Options ("*bolditalic(N)~"= 758)")),
             graphwidth = unit(150, "mm"),
             colgap = unit(25, "mm"))

plot_preferred_relationship_options_robust
```


## Partner preferences
```{r}
base_data_prefs_robust <- tibble(mean  = c(-0.43, -0.63, -0.70, -0.10, -0.24, -0.05), 
                                 lower = c(-0.55, -0.77, -0.84, -0.23, -0.37, -0.18),
                                 upper = c(-0.30, -0.49, -0.57, -0.03, -0.11, 0.08),
                                 Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                                 d = c("-0.43", "-0.63", "-0.70", "-0.10", "-0.24", "-0.05"))


header_prefs_robust <- tibble(Partner_preferences = c("", "Outcome"),
                d = c("", "d"),
                 summary = TRUE)


partner_preferences_prefs_robust <- bind_rows(header_prefs_robust,
                                base_data_prefs_robust)



plot_partner_preferences_robust = partner_preferences_prefs_robust %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-2,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5,-1, -0.5, -0.26,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab = gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Ideal Long-Term Partner Preferences ("*bolditalic(N)~"= 780)")),
             graphwidth = unit(150, "mm"))

plot_partner_preferences_robust
```

## Self-ratings
```{r}
base_data_self_robust <- tibble(mean  = c(-0.46, -0.49, -0.65, -0.39, -0.45, -0.18), 
                                lower = c(-0.59, -0.62, -0.78, -0.52, -0.58, -0.31),
                                upper = c(-0.33, -0.35, -0.53, -0.25, -0.32, -0.06),
                                self_ratings = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                                d = c("-0.46", "-0.49", "-0.65", "-0.39", "-0.45", "-0.18"))

header_self_robust <- tibble(self_ratings = c("", "Outcome"),
                d = c("", "d"),
                 summary = TRUE)

self_ratings_robust <- bind_rows(header_self_robust,
                          base_data_self_robust)

plot_self_ratings_robust = self_ratings_robust %>% 
  forestplot(labeltext = c(self_ratings, d), 
             graph.pos = 3,
              clip = c(-2,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5,-1, -0.5, -0.26,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Self-Ratings ("*bolditalic(N)~"= 772)")),
             graphwidth = unit(150, "mm"))

plot_self_ratings_robust
```

# Forest plots for additional analyses (controllign for relationship interests)
## 1) Controlling for disinterest in long-term relationship
```{r}
base_data_add <- tibble(mean  = c(-0.45, -0.49, -0.61, -0.14, -0.50, 0.03), 
                    lower = c(-0.61, -0.66, -0.77, -0.30, -0.66, -0.12),
                    upper = c(-0.30, -0.32, -0.46, 0.02, -0.33, 0.19),
                    Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.45", "-0.49", "-0.61", "-0.14", "-0.50", "0.03"))

header_add <- tibble(Partner_preferences = c("", "Partner preferences"),
                d = c("", "d"),
                 summary = TRUE)

partner_preferences_add <- bind_rows(header_add,
                                base_data_add)



partner_preferences_add %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5, -.26, -0.5,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("Controlling for disinterest in long-term relationships ("*bolditalic(N)~"= 636)")),
             graphwidth = unit(150, "mm"))
```

## 2) + interest in hook ups
### create forest plot
```{r}
base_data_add2 <- tibble(mean  = c(-0.49, -0.43, -0.37, -0.23, -0.44, -0.04), 
                    lower = c(-0.65, -0.60, -0.52, -0.38, -0.60, -0.19),
                    upper = c(-0.33, -0.27, -0.22, -0.08, -0.28, 0.11),
                    Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.49", "-0.43", "-0.37", "-0.23", "-0.44", "-0.04"))

header_add2 <- tibble(Partner_preferences = c("", "Partner preferences"),
                d = c("", "d"),
                 summary = TRUE)

partner_preferences_add2 <- bind_rows(header_add2,
                                base_data_add2)



partner_preferences_add2 %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5, -.26, -0.5,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("+ Interest in purely sexual relationships ("*bolditalic(N)~"= 636)")),
             graphwidth = unit(150, "mm"))
```

## 3) + Interest in becoming a parent
#### create forest plot
```{r}
base_data_add3 <- tibble(mean  = c(-0.35, -0.43, -0.59, -0.06, -0.33, 0.05), 
                    lower = c(-0.51, -0.59, -0.76, -0.22, -0.49, -0.11),
                    upper = c(-0.20, -0.27, -0.43, 0.10, -0.17, 0.20),
                    Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.35", "-0.43", "-0.59", "-0.06", "-0.33", "0.05"))

header_add3 <- tibble(Partner_preferences = c("", "Partner preferences"),
                d = c("", "d"),
                 summary = TRUE)

partner_preferences_add3 <- bind_rows(header_add3,
                                base_data_add3)


partner_preferences_add3 %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "darkblue")), 
             xticks = c(-1.5, -.26, -0.5,0, .26, .5, 1, 1.5),
             xlab = "Effect size (Cohen's d)",
             txt_gp = fpTxtGp(ticks=gpar(cex=.75), xlab=gpar(cex=1)),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             title = expression(bold("+ Parenting interest ("~bolditalic(N)~" = 634)")),
             graphwidth = unit(150, "mm"))


```



### Ausprobieren
## Preferred relationship options
```{r}
base_data <- tibble(mean  = c(-0.67, 1.12, -0.46, 0.20, 0.57, 0.61, -0.77), 
                    lower = c(-0.83, 0.93, -0.61, 0.05, 0.41, 0.45, -0.94),
                    upper = c(-0.51, 1.32, -0.31, 0.35, 0.73, 0.76, -0.61),
                    Preferred_relationship_options = c("Sexual, non-romantic", "Non-sexual, romantic", "Monogamous", "Non-monogamous", "Alternative committed", "Being non-partnered", "Becoming a parent"),
                    d = c("-0.67", "1.12", "-0.46", "0.20", "0.57", "0.61", "-0.77"))

summary <- tibble(mean  = 0.09,
                  lower = 0,
                  upper = 0.5,
                  Preferred_relationship_options = "Summary",
                  d = "0.09",
                  summary = TRUE)

header <- tibble(Preferred_relationship_options = c("", "Preferred relationship options"),
                d = c("", "d"),
                 summary = TRUE)

empty_row <- tibble(mean = NA_real_)

preferred_relationship_options <- bind_rows(header,
                                base_data,
                                empty_row,
                                summary)



preferred_relationship_options  %>% 
  forestplot(labeltext = c(Preferred_relationship_options, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.1, .1), 
                              gp = gpar(lty = 2, col = "#CCCCFF")), 
              xticks = c(-.1, -0.5, -0.1,0, .1, .5, 1),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"),
             xlab = "Effect size (Cohen's d)")
```


## Partner preferences
```{r}
base_data_prefs <- tibble(mean  = c(-0.37, -0.52, -0.66, -0.16, -0.21, 0.01), 
                    lower = c(-0.51, -0.66, -0.81, -0.30, -0.35, -0.12),
                    upper = c(-0.24, -0.37, -0.51, -0.02, -0.08, 0.15),
                    Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.37", "-0.52", "-0.66", "0.16", "-0.21", "0.01"))

round(mean(base_data_prefs$mean),2) # mean of means

summary <- tibble(mean  = -0.32,
                  lower = -.5,
                  upper = 0.5,
                  Partner_preferences = "Summary",
                  d = "-0.32",
                  summary = TRUE)

header <- tibble(Partner_preferences = c("", "Partner preferences"),
                d = c("", "d"),
                 summary = TRUE)

empty_row <- tibble(mean = NA_real_)

partner_preferences <- bind_rows(header,
                                base_data_prefs,
                                empty_row,
                                summary)



partner_preferences %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.1, .1), 
                              gp = gpar(lty = 2, col = "#CCCCFF")), 
             xticks = c(-.1, -0.5, -0.1,0, .1, .5, 1),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"))
```


## Self-ratings
```{r}
base_data_self <- tibble(mean  = c(-0.43, -0.49, -0.65, -0.40, -0.45, -0.17), 
                    lower = c(-0.57, -0.63, -0.79, -0.54, -0.60, -0.31),
                    upper = c(-0.29, -0.34, -0.52, -0.25, -0.31, -0.04),
                    self_ratings = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.43", "-0.49", "-0.65", "-0.40", "-0.45", "-0.17"))

round(mean(base_data_self$mean),2) # mean of means


header <- tibble(self_ratings = c("", "Self-ratings"),
                d = c("", "d"),
                 summary = TRUE)


self_ratings <- bind_rows(header,
                                base_data_self)



self_ratings %>% 
  forestplot(labeltext = c(self_ratings, d), 
             graph.pos = 3,
              clip = c(-2,2),
             lty.ci = 2,
             boxsize = .25,
             ## Preferred relationship options
```{r}
base_data <- tibble(mean  = c(-0.67, 1.12, -0.46, 0.20, 0.57, 0.61, -0.77), 
                    lower = c(-0.83, 0.93, -0.61, 0.05, 0.41, 0.45, -0.94),
                    upper = c(-0.51, 1.32, -0.31, 0.35, 0.73, 0.76, -0.61),
                    Preferred_relationship_options = c("Sexual, non-romantic", "Non-sexual, romantic", "Monogamous", "Non-monogamous", "Alternative committed", "Being non-partnered", "Becoming a parent"),
                    d = c("-0.67", "1.12", "-0.46", "0.20", "0.57", "0.61", "-0.77"))

summary <- tibble(mean  = 0.09,
                  lower = 0,
                  upper = 0.5,
                  Preferred_relationship_options = "Summary",
                  d = "0.09",
                  summary = TRUE)

header <- tibble(Preferred_relationship_options = c("", "Preferred relationship options"),
                d = c("", "d"),
                 summary = TRUE)

empty_row <- tibble(mean = NA_real_)

preferred_relationship_options <- bind_rows(header,
                                base_data,
                                empty_row,
                                summary)



preferred_relationship_options  %>% 
  forestplot(labeltext = c(Preferred_relationship_options, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.1, .1), 
                              gp = gpar(lty = 2, col = "#CCCCFF")), 
              xticks = c(-.1, -0.5, -0.1,0, .1, .5, 1),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"))
```


## Partner preferences
```{r}
base_data_prefs <- tibble(mean  = c(-0.37, -0.52, -0.66, -0.16, -0.21, 0.01), 
                    lower = c(-0.51, -0.66, -0.81, -0.30, -0.35, -0.12),
                    upper = c(-0.24, -0.37, -0.51, -0.02, -0.08, 0.15),
                    Partner_preferences = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.37", "-0.52", "-0.66", "0.16", "-0.21", "0.01"))

round(mean(base_data_prefs$mean),2) # mean of means

summary <- tibble(mean  = -0.32,
                  lower = -.5,
                  upper = 0.5,
                  Partner_preferences = "Summary",
                  d = "-0.32",
                  summary = TRUE)

header <- tibble(Partner_preferences = c("", "Partner preferences"),
                d = c("", "d"),
                 summary = TRUE)

empty_row <- tibble(mean = NA_real_)

partner_preferences <- bind_rows(header,
                                base_data_prefs,
                                empty_row,
                                summary)



partner_preferences %>% 
  forestplot(labeltext = c(Partner_preferences, d), 
             graph.pos = 3,
              clip = c(-1,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.1, .1), 
                              gp = gpar(lty = 2, col = "#CCCCFF")), 
             xticks = c(-.1, -0.5, -0.1,0, .1, .5, 1),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"))
```


## Self-ratings
```{r}
base_data_self <- tibble(mean  = c(-0.43, -0.49, -0.65, -0.40, -0.45, -0.17), 
                    lower = c(-0.57, -0.63, -0.79, -0.54, -0.60, -0.31),
                    upper = c(-0.29, -0.34, -0.52, -0.25, -0.31, -0.04),
                    self_ratings = c("Confident-assertive", "Attractive", "Sexually experienced", "Kind-supportive", "Financially secure-successful", "Educated-intelligent"),
                    d = c("-0.43", "-0.49", "-0.65", "-0.40", "-0.45", "-0.17"))

round(mean(base_data_self$mean),2) # mean of means

summary <- tibble(mean  = -0.43,
                  lower = -.5,
                  upper = 0.5,
                  self_ratings = "Summary",
                  d = "-0.43",
                  summary = TRUE)

header <- tibble(self_ratings = c("", "Self-ratings"),
                d = c("", "d"),
                 summary = TRUE)

empty_row <- tibble(mean = NA_real_)

self_ratings <- bind_rows(header,
                                base_data_self,
                                empty_row,
                                summary)



self_ratings %>% 
  forestplot(labeltext = c(self_ratings, d), 
             graph.pos = 3,
              clip = c(-2,2),
             lty.ci = 2,
             boxsize = .25,
              is.summary = summary,
              grid = structure(c(-.26, .26), 
                              gp = gpar(lty = 2, col = "#CCCCFF")), 
             xticks = c(-1, -0.5,-0.26, 0, 0.26, .5, 1),
             col = fpColors(box = "royalblue",
                            line = "black",
                            summary = "royalblue"))

```
