---
title: "xx"
output: html_document
date: '2022-07-26'
editor_options: 
  chunk_output_type: console
---

# Which file used which packages?
# load package NCmisc
```{r}
library(NCmisc)
```

## 00_data_wrangling
```{r}
# knitr::purl("00_data_wrangling.Rmd")
list.functions.in.file("00_data_wrangling.R")
```
base, utils, stats
dplyr, formr

## 01_exclusion
```{r}
# knitr::purl("01_exclusion.Rmd")
list.functions.in.file("01_exclusion.R")
```
base, utils, stats, dplyr, tidyr

## 01_excluded_vs_included
```{r}
# knitr::purl("01_excluded_vs_included.Rmd")
list.functions.in.file("01_excluded_vs_included.R")
```
base, utils, stats, graphics, dplyr, effsize/psych

## 02_codebook
```{r}
# knitr::purl("02_codebook.Rmd")
list.functions.in.file("02_codebook.R")
```
base, utils, dplyr, ggplot2

## 03_codebook_robustness
```{r}
# knitr::purl("03_codebook_robustness.Rmd")
list.functions.in.file("03_codebook_robustness.R")
```
base, utils, dplyr, ggplot2

## 04_descriptives_before_matching
```{r}
# knitr::purl("04_descriptives_before_matching.Rmd")
list.functions.in.file("04_descriptives_before_matching.R")
```
base, utils, stats, graphics, dplyr, psych, ggplot2

## 05_psm
```{r}
# knitr::purl("05_psm.Rmd")
list.functions.in.file("05_psm.R")
```
base, utils, stats, graphics, psych, dplyr, 
Matchit
cobalt

## 06_robustness_psm
```{r}
knitr::purl("06_robustness_psm.Rmd")
list.functions.in.file("06_robustness_psm.R")
```
base, utils, stats, graphics, psych, dplyr, 
Matchit
cobalt

## 07_

## 08_descriptives_psm
```{r}
# knitr::purl("08_descriptives_psm.Rmd")
list.functions.in.file("08_descriptives_psm.R")
```
base, stats, utils, graphics
apaTables
dplyr, psych ggplot2

## 09_

## 10_analyses
```{r}
# knitr::purl("10_analyses.Rmd")
list.functions.in.file("10_analyses.R")
```
base, utils, stats
dplyr, ggplot2, psych
gridExtra

## 11_comparison_matched_unmatched
```{r}
# knitr::purl("11_comparison_matched_unmatched.Rmd")
list.functions.in.file("11_comparison_matched_unmatched.R")
```
base, utils, stats
psych, effsize, dplyr, ggplot2, 
rcompanion, confintr

## 12_robustness_analyses
```{r}
# knitr::purl("12_robustness_analyses.Rmd")
list.functions.in.file("12_robustness_analyses.R")
```
base, stats, graphics, 
dplyr, psych, effsize
?bal.tab --> cobalt package nicht geladen???

# 13_sensitivity_analyses
```{r}
knitr::purl("13_sensitivity_analyses.Rmd")
list.functions.in.file("13_sensitivity_analyses.R")
```
base, stats, utils, 
dplyr, effsize/psych
MatchIt
EValue
rbounds

# 14_analyses_additional
```{r}
knitr::purl("14_analyses_additional.Rmd")
list.functions.in.file("14_analyses_additional.R")
```
base, graphics, utils, stats
ggplot2, grid, dplyr, effsize, psych
forestplot
cobalt
MatchIt

# 15_lifetime_sexual_partners
```{r}
knitr::purl("15_lifetime_sexual_partners.Rmd")
list.functions.in.file("15_lifetime_sexual_partners.R")
```
base, stats, utils
effsize, psych, dplyr, ggplot2


# 16_forest_plot
```{r}
knitr::purl("16_forest_plot.Rmd")
list.functions.in.file("16_forest_plot.R")
```
@Problem

